\bf Excuse me, do you have a moment to talk about version control?

### 2017-06-30 README.Rmd
Add push-pull figure; move random notes elsewhere

The files in a project arise in different ways and play different roles. A critical issue for workflow happiness is to figure out how you want to handle different file types with respect to Git. You can direct Git to ignore specific files or file types, such as autosaves created by your editor. This reduces noise and clutter: Git will not pester you to commit changes to these files and they will not appear in your GitHub repository. A file that Git does not ignore is said to be __tracked__. Here's a useful framework for thinking about what to track:

@@

**Intermediates:** These files are programmatically generated and serve a temporary purpose, but are not intrinsically valuable (e.g., `.aux` and `.log` in LaTex workflows).

@@

**Will it actively cause problems with Git/GitHub?** This boils down to the file's likely effect on Git operations. A file that is large and changing often can make your repository bloated and slow down pushes and pulls. If a file is binary, such as a Word document or Excel spreadsheet, you will not get human-readable diffs anyway, nor can GitHub display the content in the browser. Binary files are also a reliable source of merge conflicts (see below), because they are beyond the reach of Git's sophisticated automatic merging logic. A large binary file that changes often is, therefore, the worst of all worlds. This implies that adoption of Git/GitHub rewards a pivot away from `.docx`, `.xlsx`, and `.pdf` as primary file formats and towards `.Rmd`, `.md`, and `.csv`, at least during periods of rapid development.

@@

Managing a project via Git/GitHub is much more like the Google Doc scenario, but also offers some of the attractive features of "edit, save, attach". With Git/GitHub, collaborators can work offline and there can be independent lines of development, i.e. branches. The killer feature is that Git/GitHub enable regular and structured reconciliation of all versions of all the files in the project. It is definitely more complicated than collaborating on a Google Doc, but also more powerful.

@@

Git is a decentralized version control system, meaning each collaborator has their own complete copy of the repo and its history. Everyone can work offline and/or simultaneously. GitHub plays the role of another collaborator, but a very special one. By convention, everyone agrees that GitHub is the clearinghouse, i.e. it holds the master copy of the project. The joke is that GitHub puts the "central" in decentralized version control. You pull regularly from GitHub, to receive and integrate changes made by your collaborators. You also push regularly to GitHub, to return the favor, and to maintain its status as the comprehensive, authoritative version of the project.

@@

*inspiration for possible figures on collaboration/merging and the role of a remote, from the barlett talk*

```{r echo = FALSE, out.width="100%"}
knitr::include_graphics("bartlett-pull.png")
```

@@

@@

## Random things lying around

Consider links to GitHub repos that exemplify certain points and are very unlikely to disappear any time soon.n

possible github explainer
https://www.wired.com/2015/03/github-conquered-google-microsoft-everyone-else/

http://stackoverflow.com/questions/2712421/r-and-version-control-for-the-solo-data-analyst

https://www.onshape.com/cad-blog/how-google-solved-the-version-control-problem

https://github.com/blog/2289-publishing-with-github-pages-now-as-easy-as-1-2-3

A Quick Introduction to Version Control with Git and GitHub
http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1004668

The active R package development community on GitHub.

  * If you care deeply about someone else's project, such as an R package you use heavily, you can track its development on GitHub. You can watch the repository to get notified of major activity. You can fork it to keep your own copy. You can modify your fork to add features or fix bugs and send them back to the owner as a proposed change.

The read-only mirrors of R source and all of CRAN. Coupled with GitHub search features, you can answer alot of your own questions this way.

instructions re: supplementary materials
http://amstat.tfjournals.com/supplementary-materials/

TAS author instructions
http://www.tandfonline.com/action/authorSubmission?journalCode=utas20&page=instructions

http://mynameismichelle.com/git-frost/

*These two points were originally written as comparisons with Google Docs, but now there are intervening paragraphs. I think I will cut them.*

*Manage multiple files*. A Git repository is inherently multi-file and therefore well suited to projects comprised of many files, evolving in a coordinated fashion. Examples include a data analysis, a course website, a blog, an R package, or a book. If there is any way to proactively check or enforce their joint functionality, this is something you could verify manually prior to a commit or at certain milestones. In the case of a website, you might choose to rebuild the site prior to a commit. In the case of an R package, `R CMD check` is one of the easiest things to automate on GitHub.

*Diffs and time travel*. Google Docs are fantastic for simple collaborative work, when you don't need detailed access to the history. But the version control offered by Google Drive is very limited compared to Git. You can't compare versions at arbitrary points in time, temporarily checkout previous versions, or maintain two lines of development.

*May need a segue ... depends on the fate of the two paragraphs above.*

```{r eval = FALSE, echo = FALSE, results = 'asis'}
cat("*here's one way I see phylogeny in my mind*\n")
cat("![](https://upload.wikimedia.org/wikipedia/commons/2/2b/Phylogeny_of_Retroviruses.jpg)")

cat("\n\n*make such a phylogeny with a set of crazy filenames like this*\n") 
cat("![](https://www.onshape.com/hs-fs/hub/379003/file-2533844795-jpg/Blog_Assets/Version_Control_Graphic-2.jpg?t=1494963046029)")

cat("\n\n*or riff on the famous PhD Comic*") 
cat("![](http://phdcomics.com/comics/archive/phd101212s.gif)")
```

>>>>

The files in a project arise in different ways and play different roles. A critical issue for workflow happiness is to decide how to handle different file types with respect to Git. You can direct Git to ignore specific files or file types, such as autosaves created by your editor. This reduces noise and clutter: Git will not pester you to commit changes to these files and they will not appear in your GitHub repository. A file that Git does not ignore is said to be __tracked__. Here's a useful framework for deciding what to track:

@@

__Intermediates:__ These files are programmatically generated and serve a temporary purpose, but are not intrinsically valuable (e.g., `.aux` and `.log` in LaTex workflows).

@@

**Will it actively cause problems with Git/GitHub?** This boils down to the file's likely effect on Git operations. A file that is large and changing often can make your repository bloated and slow down pushes and pulls. If a file is binary, such as a Word document or Excel spreadsheet, you will not get human-readable diffs anyway, nor can GitHub display the content in the browser. Binary files are also a reliable source of merge conflicts (see below), because they are beyond the reach of Git's sophisticated automatic merging logic. A large binary file that changes often is, therefore, the worst of all worlds. This implies that adoption of Git/GitHub suggests a pivot away from `.docx`, `.xlsx`, and `.pdf` as primary file formats and towards `.Rmd`, `.md`, and `.csv`, at least during periods of rapid development.

@@

Managing a project via Git/GitHub is much more like the Google Doc scenario, but also offers some of the attractive features of "edit, save, attach". With Git/GitHub, collaborators can work offline and there can be independent lines of development, i.e. branches. The killer feature is that Git/GitHub enables regular and structured reconciliation of all versions of all the files in the project. It is definitely more complicated than collaborating on a Google Doc, but also more powerful.

@@

Git is a decentralized version control system, meaning each collaborator has their own complete copy of the repo and its history. Everyone can work offline and/or simultaneously. GitHub plays the role of another collaborator, but a very special one. By convention, everyone agrees that GitHub is the clearinghouse, i.e. it holds the master copy of the project. The joke is that GitHub puts the "central" in decentralized version control. You pull regularly from GitHub, to receive and integrate changes made by your collaborators. You also push regularly to GitHub, to return the favor, and to maintain its status as the comprehensive, authoritative version of the project. Figure \ref{fig:push-pull} depicts this process.

```{r push-pull, fig.cap = "\\label{fig:push-pull}One contributor has made two new commits and updates the master copy on GitHub with a push. Another contributor stays up-to-date with a pull from GitHub."}
knitr::include_graphics("push-pull.png")
```

@@

@@

*inspiration for possible figure on collaboration/mergin, from the barlett talk*

@@

### 2017-06-30 README.tex
Add push-pull figure; move random notes elsewhere

The files in a project arise in different ways and play different roles.
A critical issue for workflow happiness is to figure out how you want to
handle different file types with respect to Git. You can direct Git to
ignore specific files or file types, such as autosaves created by your
editor. This reduces noise and clutter: Git will not pester you to
commit changes to these files and they will not appear in your GitHub
repository. A file that Git does not ignore is said to be
\textbf{tracked}. Here's a useful framework for thinking about what to
track:

@@

\textbf{Will it actively cause problems with Git/GitHub?} This boils
down to the file's likely effect on Git operations. A file that is large
and changing often can make your repository bloated and slow down pushes
and pulls. If a file is binary, such as a Word document or Excel
spreadsheet, you will not get human-readable diffs anyway, nor can
GitHub display the content in the browser. Binary files are also a
reliable source of merge conflicts (see below), because they are beyond
the reach of Git's sophisticated automatic merging logic. A large binary
file that changes often is, therefore, the worst of all worlds. This
implies that adoption of Git/GitHub rewards a pivot away from
\texttt{.docx}, \texttt{.xlsx}, and \texttt{.pdf} as primary file
formats and towards \texttt{.Rmd}, \texttt{.md}, and \texttt{.csv}, at
least during periods of rapid development.

@@

Managing a project via Git/GitHub is much more like the Google Doc
scenario, but also offers some of the attractive features of ``edit,
save, attach''. With Git/GitHub, collaborators can work offline and
there can be independent lines of development, i.e.~branches. The killer
feature is that Git/GitHub enable regular and structured reconciliation
of all versions of all the files in the project. It is definitely more
complicated than collaborating on a Google Doc, but also more powerful.

@@

Git is a decentralized version control system, meaning each collaborator
has their own complete copy of the repo and its history. Everyone can
work offline and/or simultaneously. GitHub plays the role of another
collaborator, but a very special one. By convention, everyone agrees
that GitHub is the clearinghouse, i.e.~it holds the master copy of the
project. The joke is that GitHub puts the ``central'' in decentralized
version control. You pull regularly from GitHub, to receive and
integrate changes made by your collaborators. You also push regularly to
GitHub, to return the favor, and to maintain its status as the
comprehensive, authoritative version of the project.

@@

\emph{inspiration for possible figures on collaboration/merging and the
role of a remote, from the barlett talk}

\includegraphics[width=1\linewidth]{bartlett-pull}

@@

@@

\subsection{Random things lying
around}\label{random-things-lying-around}

Consider links to GitHub repos that exemplify certain points and are
very unlikely to disappear any time soon.n

possible github explainer
\url{https://www.wired.com/2015/03/github-conquered-google-microsoft-everyone-else/}

\url{http://stackoverflow.com/questions/2712421/r-and-version-control-for-the-solo-data-analyst}

\url{https://www.onshape.com/cad-blog/how-google-solved-the-version-control-problem}

\url{https://github.com/blog/2289-publishing-with-github-pages-now-as-easy-as-1-2-3}

A Quick Introduction to Version Control with Git and GitHub
\url{http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1004668}

The active R package development community on GitHub.

\begin{itemize}
\tightlist
\item
  If you care deeply about someone else's project, such as an R package
  you use heavily, you can track its development on GitHub. You can
  watch the repository to get notified of major activity. You can fork
  it to keep your own copy. You can modify your fork to add features or
  fix bugs and send them back to the owner as a proposed change.
\end{itemize}

The read-only mirrors of R source and all of CRAN. Coupled with GitHub
search features, you can answer alot of your own questions this way.

instructions re: supplementary materials
\url{http://amstat.tfjournals.com/supplementary-materials/}

TAS author instructions
\url{http://www.tandfonline.com/action/authorSubmission?journalCode=utas20\&page=instructions}

\url{http://mynameismichelle.com/git-frost/}

\emph{These two points were originally written as comparisons with
Google Docs, but now there are intervening paragraphs. I think I will
cut them.}

\emph{Manage multiple files}. A Git repository is inherently multi-file
and therefore well suited to projects comprised of many files, evolving
in a coordinated fashion. Examples include a data analysis, a course
website, a blog, an R package, or a book. If there is any way to
proactively check or enforce their joint functionality, this is
something you could verify manually prior to a commit or at certain
milestones. In the case of a website, you might choose to rebuild the
site prior to a commit. In the case of an R package,
\texttt{R\ CMD\ check} is one of the easiest things to automate on
GitHub.

\emph{Diffs and time travel}. Google Docs are fantastic for simple
collaborative work, when you don't need detailed access to the history.
But the version control offered by Google Drive is very limited compared
to Git. You can't compare versions at arbitrary points in time,
temporarily checkout previous versions, or maintain two lines of
development.

\emph{May need a segue \ldots{} depends on the fate of the two
paragraphs above.}

>>>>

The files in a project arise in different ways and play different roles.
A critical issue for workflow happiness is to decide how to handle
different file types with respect to Git. You can direct Git to ignore
specific files or file types, such as autosaves created by your editor.
This reduces noise and clutter: Git will not pester you to commit
changes to these files and they will not appear in your GitHub
repository. A file that Git does not ignore is said to be
\textbf{tracked}. Here's a useful framework for deciding what to track:

@@

\textbf{Will it actively cause problems with Git/GitHub?} This boils
down to the file's likely effect on Git operations. A file that is large
and changing often can make your repository bloated and slow down pushes
and pulls. If a file is binary, such as a Word document or Excel
spreadsheet, you will not get human-readable diffs anyway, nor can
GitHub display the content in the browser. Binary files are also a
reliable source of merge conflicts (see below), because they are beyond
the reach of Git's sophisticated automatic merging logic. A large binary
file that changes often is, therefore, the worst of all worlds. This
implies that adoption of Git/GitHub suggests a pivot away from
\texttt{.docx}, \texttt{.xlsx}, and \texttt{.pdf} as primary file
formats and towards \texttt{.Rmd}, \texttt{.md}, and \texttt{.csv}, at
least during periods of rapid development.

@@

Managing a project via Git/GitHub is much more like the Google Doc
scenario, but also offers some of the attractive features of ``edit,
save, attach''. With Git/GitHub, collaborators can work offline and
there can be independent lines of development, i.e.~branches. The killer
feature is that Git/GitHub enables regular and structured reconciliation
of all versions of all the files in the project. It is definitely more
complicated than collaborating on a Google Doc, but also more powerful.

@@

Git is a decentralized version control system, meaning each collaborator
has their own complete copy of the repo and its history. Everyone can
work offline and/or simultaneously. GitHub plays the role of another
collaborator, but a very special one. By convention, everyone agrees
that GitHub is the clearinghouse, i.e.~it holds the master copy of the
project. The joke is that GitHub puts the ``central'' in decentralized
version control. You pull regularly from GitHub, to receive and
integrate changes made by your collaborators. You also push regularly to
GitHub, to return the favor, and to maintain its status as the
comprehensive, authoritative version of the project. Figure
\ref{fig:push-pull} depicts this process.

\begin{figure}
\includegraphics[width=1\linewidth]{push-pull} \caption{\label{fig:push-pull}One contributor has made two new commits and updates the master copy on GitHub with a push. Another contributor stays up-to-date with a pull from GitHub.}\label{fig:push-pull}
\end{figure}

@@

@@

\emph{inspiration for possible figure on collaboration/mergin, from the
barlett talk}

@@
